A new machine-learning-based prediction of survival in patients with end-stage liver disease

### 2022-11-27 analysis/elasticnet.Rmd
feat: add MELD 3.0 score

ps <- lapply(
    zlog_data[paste0("SurvProbMeld", c("Unos", "NaUnos", "Plus7"))],
    function(p) {
        ctpnts <- cutpoints(p, n = ameldcfg$m)
        f <- cut(p, ctpnts, include.lowest = TRUE)
        list(
            predicted = groupmean(p, f = f),
            observed = observed_survival(
                amelddata$y, f = f, times = ameldcfg$times
            )
        )
    }
)
names(ps) <- c("MELD", "MELD-Na", "MELD-Plus7")
col <- viridisLite::viridis(6)[4:6]

@@

ps <- lapply(
    zlog_data_complete_cases[paste0("SurvProbMeld", c("Unos", "NaUnos", "Plus7"))],
    function(p) {
        ctpnts <- cutpoints(p, n = ameldcfg$m)
        f <- cut(p, ctpnts, include.lowest = TRUE)
        list(
            predicted = groupmean(p, f = f),
            observed = observed_survival(
                amelddatacc$y, f = f, times = ameldcfg$times
            )
        )
    }
)
names(ps) <- c("MELD", "MELD-Na", "MELD-Plus7")
col <- viridisLite::viridis(6)[4:6]

>>>>

ps <- lapply(
    zlog_data[paste0("SurvProbMeld", c("Unos", "NaUnos", "3", "Plus7"))],
    function(p) {
        ctpnts <- cutpoints(p, n = ameldcfg$m)
        f <- cut(p, ctpnts, include.lowest = TRUE)
        list(
            predicted = groupmean(p, f = f),
            observed = observed_survival(
                amelddata$y, f = f, times = ameldcfg$times
            )
        )
    }
)
names(ps) <- c("MELD", "MELD-Na", "MELD 3.0", "MELD-Plus7")
col <- viridisLite::viridis(7)[4:7]

@@

ps <- lapply(
    zlog_data_complete_cases[paste0("SurvProbMeld", c("Unos", "NaUnos", "3", "Plus7"))],
    function(p) {
        ctpnts <- cutpoints(p, n = ameldcfg$m)
        f <- cut(p, ctpnts, include.lowest = TRUE)
        list(
            predicted = groupmean(p, f = f),
            observed = observed_survival(
                amelddatacc$y, f = f, times = ameldcfg$times
            )
        )
    }
)
names(ps) <- c("MELD", "MELD-Na", "MELD 3.0", "MELD-Plus7")
col <- viridisLite::viridis(7)[4:7]

### 2022-11-27 analysis/histograms.Rmd
feat: add MELD 3.0 score

```{r histograms_meld, results = "asis", message = FALSE, warning = FALSE}
meldv <-
    c(paste0("ScoreMeld", c("", "Unos", "Na", "NaUnos")),
      paste0("SurvProbMeld", c("Unos", "NaUnos", "Plus7")))
for (v in meldv) {
    cat("\n\n##", v , "\n\n")
    .hist(zlog_data[[v]], main = paste0("Histogram of ", v), xlab = v)
    .qqnorm(zlog_data[[v]], yname = v)
}
```

>>>>

```{r histograms_meld, results = "asis", message = FALSE, warning = FALSE}
meldv <-
    c(paste0("ScoreMeld", c("", "Unos", "Na", "NaUnos", "3")),
      paste0("SurvProbMeld", c("Unos", "NaUnos", "3", "Plus7")))
for (v in meldv) {
    cat("\n\n##", v , "\n\n")
    .hist(zlog_data[[v]], main = paste0("Histogram of ", v), xlab = v)
    .qqnorm(zlog_data[[v]], yname = v)
}
```

### 2022-11-27 analysis/supplement.Rmd
feat: add MELD 3.0 score

```{r roc-plot, echo = FALSE, fig.width = 18, fig.height = 12, fig.cap = "Trend in the area under the time-dependent receiver operating characteristic curve (AUROC) based on the nonparametric inverse probability of censoring weighting estimate (IPCW) for AMELD, MELD, MELD-Na, and MELD-Plus7, as described in [@blanche2013]."}
tar_load(timeROC_MELD)
tar_load(timeROC_MELDNa)
tar_load(timeROC_MELDPlus7)
tar_load(timeROC_RCV)

m <- list(
    AMELD = timeROC_RCV,
    MELD = timeROC_MELD,
    "MELD-Na" = timeROC_MELDNa,
    "MELD-Plus7" = timeROC_MELDPlus7
)
plot_surv_roc_trend(m, xlab = "time [days]", col = viridisLite::viridis(5)[-2])
```

>>>>

```{r roc-plot, echo = FALSE, fig.width = 18, fig.height = 12, fig.cap = "Trend in the area under the time-dependent receiver operating characteristic curve (AUROC) based on the nonparametric inverse probability of censoring weighting estimate (IPCW) for AMELD, MELD, MELD-Na, and MELD-Plus7, as described in [@blanche2013]."}
tar_load(timeROC_MELD)
tar_load(timeROC_MELDNa)
tar_load(timeROC_MELD3)
tar_load(timeROC_MELDPlus7)
tar_load(timeROC_RCV)

m <- list(
    AMELD = timeROC_RCV,
    MELD = timeROC_MELD,
    "MELD-Na" = timeROC_MELDNa,
    "MELD 3.0" = timeROC_MELD3,
    "MELD-Plus7" = timeROC_MELDPlus7
)
plot_surv_roc_trend(m, xlab = "time [days]", col = viridisLite::viridis(6)[-2])
```
